A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-29 0_reviewer_response.tex

\paper{4. Beading schemes, end of section}{
\paragraph{Widening \revise{}{meta-scheme}}
Complementary to any of these schemes we can enforce a minimum feature size \revise{at no extra cost}{and minimum bead width} in our framework.
Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
See \cref{min_feature_size,widening}.
We can simply override
\begin{align*}
q'(d) &= 
\begin{cases}
0 & \text{ if } 0 \leq d < 2 r_\text{min} \\
1 & \text{ if }  2 r_\text{min} \leq d < w^*  \\
q(d) & \text{ otherwise}
\end{cases}
\\
W'(n,r)_0 &=
\begin{cases}
\max \left( w_\text{min}  ,  2 r \right) & \text{ if } 2 r < w^* \\
W(n,r)_0 & \text{ otherwise}
\end{cases}
\end{align*}

\revise{}{
\paragraph{Shell meta-scheme}
The industry standard of FDM is to generate only a limited contour-parallel perimeters and to fill the remainder using a direction-parallel strategy.
We therefore provide a meta-scheme to generate adaptive bead width toolpaths only in narrow regions and generate the limited number of perimeters $M$ using the preferred width in regions which are wide enough.
We also take care not to leave gaps which are too small to be filled using the direction-parallel strategy:
}

\revise{}{
\begin{align*}
q'(d) &= \min(M, q(d))
\\
W'(n,r)_i &= 
\begin{cases}
W(n, M w^*)_i & \text{ if } 2 r > q^{-1}(M) \\
W(n,r)_i & \text{ otherwise}
\end{cases}
\end{align*}
}

\revise{}{
These meta-schemes introduce non-linearities in the quantization function.
Because the beading is only evaluated at nodes in the skeleton, we need to make sure that there are nodes at the locations along the skeleton where the non-linearities happen.
We therefore insert extra nodes along with their ribs at locations $v$ with a radial distance $R(v) = r_\text{min}$ for widening and at $R(v) \in \left\{ M w^*, q^{-1}(M), q^{-1}(M) + \nicefrac12 w^* \right\} $ for the transition from narrow shell to unconstrained shell.
Combining all meta-schemes functionality we can generate results such as depicted in \cref{shell}.
}
\begin{figure}
\centering
\setlength{\figwidth}{.35\mycolumnwidth}
\setlength{\figwidthTwo}{.6\mycolumnwidth}
\begin{minipage}[b]{\figwidthTwo} \centering
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Distributed-feature-size.png}
\caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
\\ on top of the Distributed scheme}
\label{min_feature_size}
\end{subfigure}
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Center-widening.png}
\caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
\\ on top of the Center scheme}
\label{widening}
\end{subfigure}
\end{minipage}
\begin{subfigure}[b]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined.png}
\caption{Shell and widening}
\label{shell}
\end{subfigure}
\caption{
Toolpaths using the widening and shell meta-schemes.
\subref{min_feature_size} and~\subref{widening} show widening.
\subref{shell}
show toolpaths generated with the inward distributed strategy ($N=1.5$) in conjunction with the shell meta-scheme ($M=4$) and the same widening as in~\subref{widening}.
% -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
Widening and shell require extra edges (green) at key locations in the skeleton.
The azure area is to be filled using some direction-parallel toolpaths.
}
\label{widening_shell}
\end{figure}
}
\paper{6 Results and discussion}
{
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
}

@@

\Cref{no_corners} (of this document) shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by \citeauthor{Ding2016a}.
}
\begin{figure} \centering
\setlength{\figwidth}{.45\mycolumnwidth}
\begin{subfigure}[b]{\figwidth} \centering
\includegraphics[rotate=-90,width=\linewidth]{response_rects_Center_accuracy.png}
\caption{Problematic for center, i.e. \citeauthor{Jin2017JMS}, exhibiting $4.5w^*$ and $5.8w^*$}
\end{subfigure}
\begin{subfigure}[b]{\figwidth} \centering
\includegraphics[width=\linewidth]{response_no_corners}
\caption{Problematic for constant, i.e. \citeauthor{Ding2016a}}
\end{subfigure}
\caption{Example shapes without sharp corners.}
\label{no_corners}
\end{figure}

\Que{
How do the authors conduct path planning? Could the authors add a simple 2D geometry with multiple holes to explain the path planning process? As the proposed approach adds more disconnected toolpaths to minimize underfill areas, an improper path planning would significantly increase the fabrication time. 
}\label{printtime_question}
\Ans{
We now included a description of the path order algorithm, which is naive and greedy -- similar to the one employed by the software package Ultimaker Cura.
A suboptimal path planning is preferred because of a reduced computation time.
Travel times are only \SI{2}{\percent} of the total print time in our current setup, so the effect of improper path planning is negligible compared to the differences in extrusion time.

We now include statistics on extrusion time, travel time and path counts.
These new statistics are now also reflected upon in the comparison of the beading schemes.

Because the extrusion time depends on the actual printing setup we have moved the section on print results to before the statistics section.
}
\commits{
d375878a8a6d01c53436aeb9c473dbedd8f3edcf % path order algorithm
e2c940f2362556ae8d017cff63c81b4bbcb77286 % print time, path count statistics
7f567012b409445fc120968e995f861cab56e776 % new beading schemes comparison
bf403fe797193e40b004c2cae806935f699271e5 % move print results to before statistics 
b106dd1e0067114756bf96a7dc10458202380f2e % new print time pdf graph
}
\paper{5.2 Print results}{\revise{}{The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.}} 
\paper{6.1.3 Print time}
{
\revisepar{
\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We therefore measured the angle between consecutive extrusion segments generated by each scheme
and report on the occurrence of each angle in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
}{
\subsubsection{Print time}
The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the toolpaths.
In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
While the idealized print time is predominantly determined by the total toolpath length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which may introduce defects and incurs extra print time.
For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
We therefore report both on the open and closed path count in \cref{pathcounts}.
}
}
\paper{6.2 Comparison of beading schemes}
{
We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average \revise{approximately}{} \revise{\SI{1}{\percent}}{\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

@@

\Que{
While the proposed approach can use adaptive bead width to minimize underfill and overfill areas, the generated toolpaths are disconnected compared to the traditional approaches. From my experience, a small overfill area does not have to lead to serious defects. But the disconnected filaments definitely have worse mechanical performances compared to the continuous ones. 
}
\Ans{
Indeed the discontinuities are both relevant to print time and introduce defects.
We now address these facts in text and show statistics on the number of discontinuities in Fig.~18c (\cref{printtime} here).
The evenly and inward distributed schemes cause approximately \SI{20}{\percent} more discontinuities compared to the uniform method, but the print time is not significantly increased.

We have not performed a physical tests which informs on the influence of discontinuities or of overfill on the mechanical performance of any 3D printer.
Disconnected filaments will have worse mechanical performance compared to continuous ones, but we don't know how they compare against overfilling ones.
Altering the beading strategy locally depending on the size of the overfill area is in interesting idea for future research.

Without such a method we can only compare the total impact of our method compared to existing methods.
While the evenly and inward distributed schemes cost \SI{20}{\percent} more discontinuities than the uniform method, the uniform method costs approx. \SI{400}{\percent} more over- and underfill.
The cost of the discontinuities is negligible compared to the benefit of reduced over- and underfill.

Compared against the state-of-the-art centered method, our schemes only reduce the number of discontinuities.
}
\commits{
272fbca357c379ebe291735e3084cf86db4bdee1 % more emphasis on defects introduced by discontinuities
f2132c1c0cbce6daa29f64890be5f9e20c79c630 % future work notice
}
\paper{6.1.3 Print time}
{
\revise{}{
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which may introduce defects and incurs extra print time.
}
}
\paper{7.1 Future work}
{
An accurate model of manufacturability, \revise{}{which relates }print speed, \revise{}{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
}

@@

The question can also be interpreted as saying that one might use a different shape than the geometry in Fig.~1.
We decided on this wedge shape because it shows how the techniques deal with a wide range of feature sizes;
the wedge shape can be read as a graph where we can read out the resulting beading for any local feature size.
}
\commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1 53224c04ceff6c1b18a9eea6de8e7e33957b7797}
\paper{1. Introduction}{
[See caption of \cref{intro_wedge} here.]
}

\Que{
Please double check the following sentences. ”Third, the extruded path should ...”(at the second paragraph of Section~2) ”This the downward phase...” (at the last paragraph of Section~3.5) 
}
\Ans{
Thanks.
The following changes have been made.
}
\commits{eb2a5207c83dfe069d3ab3fc37bf2149b8a51964}
\paper{2. Related work}{
Third, the extruded path should cover \revise{a }{}the region of the contour without gaps.
}
\paper{3.5 Beading, Beading propagation}{
\revise{This the}{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.  
}

\Que{
In Fig.~4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
}
\Ans{
Note that the bead count is the number, not the arrow from the number.
The arrow is now a double thin line.
}
\commits{07df258c1fa618808ba9493384550021a03c83e1}
\paper{Fig.~4}
{
[See \cref{legend} here.]
}
\begin{figure}\centering
\includegraphics[width=.75\mycolumnwidth]{sources-method-legend2.pdf}
\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
\label{legend}
\end{figure}

\Que{
What are the differences between the distributed and the inward scheme in Fig.~16d and 16e? Are they the same? 
}
\Ans{
We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig.~17d and 17e, here \cref{TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy}).
The difference between inward and evenly distributed is now deemed to be so clear that the statistics graphs on the widths of the outer paths can be omitted;
Fig.~17c of the first submission is omitted from the revised manuscript.
}
\commits{735762b1e7daf31ae4465bf288ef867ded7da095 93352058a46fb391e323df16f45466adb8cad508
87b1b779b759a9ad115f3ea61243568bfa2e0cb6 % lil change in Fig 20 caption
ca322806c80ddc82c6f0c01d9ea5096b37ffcf8e % use smae rmin and N=2 in statistics
b4d03f0d8ea92ac9800794e154dc5b53e4448cab % don't compute graph for widths of outer bead
}
\paper{4. Beading schemes}
{
[See \cref{distributed_comparison} here.]
}
\begin{figure}
\centering
\setlength{\figwidth}{.8\mycolumnwidth}
\setlength{\figheight}{.3\mycolumnwidth}
\begin{minipage}[b]{0.8\linewidth}
% -p test_geometry/wedge.svg -o wedge -s nrdi -n 1.5 -a --scale 1.5
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-inward.png}
\caption{Inward distributed}
\end{subfigure}
\end{minipage}
\begin{subfigure}[t]{.1\mycolumnwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed \revise{}{and inward ($N=1.5$)} beading schemes for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}
\paper{Caption of now Fig.~17}
{
\revise{}{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
}
\paper{Caption of now Fig.~19}
{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
}
\paper{6 Results and discussion}
{
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
}
\paper{6.1.2 Uniformity}
{
\revise{
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
}{}
}

@@

\Que{
Related work acknowledges the previous work sufficiently. However, the differences between the state of the art and the presented work are not clear. More discussion on where this work stands with respect to the state of the art is required. 
}
\Ans{
We have tried to address this in response to several other reviewers' comments.
See our response to question~\ref{difference_to_jin} and question~\ref{contributions}.
We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
See also our response to question~\ref{widening_question} for clarification in the difference between Figs.~1b and 1c.
}
\commits{
004894210fbc961f82b792fc702d1b67a1a8e8e8 lil lang improvement (reviewer 3.3)
9ac2c005c2eb1c0696e2582963353b038fa71072 use limited distributed strategy in Fig.~1 (reviewer 1.6, 3.3)
}

\Que{
Isn’t it possible to put bounds on the width in the existing methods, such as the approach described in [9]? More discussion on that would be helpful. 
}
\Ans{
The bead width in \citeauthor{Jin2017JMS} is limited to the interval $[0.25 w^*,1.8 w^*]$, whereas ours is limited to $[0.75 w^*, 1.5 w^*]$.

### 2020-01-29 0_reviewer_response.tex

In the old manuscript we referred to the `deviation' from the preferred width as $1.8w^*/w^*=1.8$, wich was a confusing statistic.
Moreover, instead of the actual $1.8$ used by \citeauthor{Jin2017JMS} we used the theoretically maximum value of $2.0$ to arrive at a `deviation factor' of $2$.
We now don't refer to any such confusing statistic and instead just mention the range of widths itself.
}
\commits{
661d8f6766548c287cb174070432097e396d198f 
92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d give bounds on width variation (reviewer 3.4)
2f230ea9f26f9870027e80db89eae8774f19d339 fix bounds of width variation in Jin (reviewer 3.4)
acf8bbed0e530a3038d6fea064c33e7df6f0f933 % deviation > variation
}
\paper{1. Introduction}{
The current \revise{state-of-the-art}{state of the art of contour-parallel toolpath generation} \revise{for FDM printing }{}developed by \citeauthor{Jin2017JMS}
employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths $[0.25w,1.8w]$}~\cite{Jin2017JMS},
}
\paper{3.4. Central height adjustment, Transition anchors, filtering paragraph}
{
\revise{}{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
}
\paper{6.2 Comparison of beading schemes, paragraph 3, 4}{
In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.25 w^*$ and $1.8w^*$.}

### 2020-01-29 6_2_printing_results.tex
change fabrication into its own main section

\revise{}{
\subsection{Fabrication}
In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system,
we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
A different approach might be appropriate depending on whether the filament feeder is mounted directly on the print head (a.k.a. \emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle, changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.

\subsubsection{Back pressure compensation}
Because changing the internal pressure is difficult in our setup,
we keep the internal pressure constant, and vary the movement speed instead.
%In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
One approach would be\revise{}{ to} keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
We conjecture that the filament outflow is related to the total pressure in the system,
which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
The amount of back pressure is most likely monotonically related to the requested line width.
We compensate for the back pressure using a simple linear model:

@@

\subsubsection{Print results}\label{print_results_section}
Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use
$f_0 = v_0 w_0 h $
with
$v_0=\SI{30}{\milli\meter\per\second}$, 
$w_0=\SI{0.4}{\milli\meter}$
and
$h=\SI{0.1}{\milli\meter}$.
See \cref{back_pressure}.
The fact that the printed lines are wider than intended is compensated for using a flow reduction to \SI{90}{\percent}.
%
Test prints were performed on an unmodified Ultimaker S5 system,
with a standard  \SI{0.4}{\milli\meter} nozzle
and PLA filament.
The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,
we discretize adaptive width extrusions into \SI{0.2}{\milli\meter} long segments of the average width.
The print results can be viewed in \cref{prints}.

>>>>

\revise{}{
\section{Fabrication}
In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system,
we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
A different approach might be appropriate depending on whether the filament feeder is mounted directly on the print head (a.k.a. \emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle, changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.

\subsection{Back pressure compensation}
Because changing the internal pressure is difficult in our setup,
we keep the internal pressure constant, and vary the movement speed instead.
%In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
One approach would be\revise{}{ to} keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
We conjecture that the filament outflow is related to the total pressure in the system,
which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
The amount of back pressure is most likely monotonically related to the requested line width.
We compensate for the back pressure using a simple linear model:

@@

\subsection{Print results}\label{print_results_section}
Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use
$f_0 = v_0 w_0 h $
with
$v_0=\SI{30}{\milli\meter\per\second}$, 
$w_0=\SI{0.4}{\milli\meter}$
and
$h=\SI{0.1}{\milli\meter}$.
See \cref{back_pressure}.
The fact that the printed lines are wider than intended is compensated for using a flow reduction to \SI{90}{\percent}.
%
Test prints were performed on an unmodified Ultimaker S5 system,
with a standard  \SI{0.4}{\milli\meter} nozzle
and PLA filament.
The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,
we discretize adaptive width extrusions into \SI{0.2}{\milli\meter} long segments of the average width.
The print results can be viewed in \cref{prints}.

### 2020-01-29 6_validation.tex
change fabrication into its own main section

\input{6_2_printing_results}

\revise{}
{
\subsection{Computational results}\label{sec_computational_results}
} % tew
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}

>>>>

We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}

\subsection{Computational results}\label{sec_computational_results}
